### 2016-05-24 paper/icfp16-cameraready/overview.tex
cite heuristics for favoring small values

Returning to @fac@, given a hole as input we will narrow the hole
to an @int@ upon reaching the @<=@ test.
%
At this point we choose a
random @int@\footnote{With standard heuristics to favor small values.}
for the instantiation and
concrete execution takes over entirely, leading us to the expected crash
in the multiplication.

>>>>

Returning to @fac@, given a hole as input we will narrow the hole
to an @int@ upon reaching the @<=@ test.
%
At this point we choose a
random @int@\footnote{With standard heuristics~\cite{Claessen2000-lj} to favor small values.}
for the instantiation and
concrete execution takes over entirely, leading us to the expected crash
in the multiplication.
